Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2017-10-30 www-2018/source/paper.tex
Updates to multipath fault tolerance.

Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure
to censorship and surveillance.
This paper presents several contributions towards advancing those goals.
While our motivation by the network of internet routers,
our work is theoretical,
and could potentially be applied to many different types of networks,
whether made of physical wires, virtual tunnels,
or other types of links.

@@

Under the above assumptions,
we show how to evaluate the influence of network structure
on attack-tolerance,
how to use local trust and redundancy to achieve greater attack-tolerance
when no single path is fully trusted,
and propose a novel routing algorithm for constructing such paths on
the butterfly network topology.
The butterfly topology is popular in parallel processing
\cite{kshemkalyani_distributed_2008} and
peer-to-peer \cite{lua_survey_2005, korzun_structured_2013}
applications, due to its regular structure, low degree, and high connectivity.

It is important to note that the butterfly is a highly structured and constrained
network topology,
very different form those found in social networks and other
self-organized networks.
The reader may wonder whether it is realistic or useful to assume such control over
the network structure.
We have already seen that whenever a single point of failure exists in the network,
there is a potential for an attacker to exploit it through coercion.
So, {\em attack-tolerance cannot be achieved without the ability to influence
network structure}.
Luckily, there are scenarios in which network topology can be dictated.
Examples include overlay networks
\cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
In general,
{\em when the need for attack-tolerance is high enough to warrant investment
in infrastructure, networks can be engineered and maintained as infrastructure}.
It is also worth noting that attack-tolerant networks may be sub-components of
larger, less-constrained systems.
For example, a single server might be replaced by a distributed network of servers,
each with different ownership, physical location, and legal jurisdiction,
without placing any unrealistic constraints on the clients connecting to
those servers.
Additionally, there may be ways to achieve improved attack-tolerance from architectures
more flexible than the butterfly, which is a potential area for future work.

We begin by describing how fault tolerance techniques can be adapted and
evaluated in a network setting with bounded trust transitivity and
adversarial faults.
Generally, faults in network paths can be correlated,
preventing the application of standard fault tolerance techniques
\cite{avizienis_basic_2004, von_neumann_probabilistic_1956},
which assume independent faults.
By constructing {\em independent paths},
which have no untrusted nodes in common,
we show how to model communication across a complex network in the presence
of correlated adversarial faults as communication across redundant
simple channels with random errors.
Redundant messages can be sent across these channels in parallel,
a technique known as {\em concurrent multipath routing}
\cite{zin_survey_2015, qadir_exploiting_2015, khiani_comparative_2013},
and used for fault tolerance.
The receiver can then use the redundant messages to detect and/or correct
errors.
We formally evaluate the
effects of network structure on attack-tolerance and show that the probability
of an undetected error decreases exponentially with the number of
independent paths between source and destination,
even when no individual path is entirely trusted.

We also propose a novel concurrent multipath routing algorithm for the butterfly
topology.
The algorithm constructs independent paths,
which can be combined with the fault-tolerant concurrent multipath routing
scheme above to
achieve a high level of adversarial fault tolerance on the butterfly topology.

Our main contributions are:
\begin{itemize}
\item{
We propose a novel method for extending standard fault tolerance techniques to
{\em adversarial} faults in {\em complex networks}.
We do so by modeling redundant independent paths
with bounded trust transitivity as a single virtual channel,
and show that the probability of detecting adversarial faults
approaches 1 exponentially with the number of paths;
}
\item{We prove that the number of $h$-internal vertex disjoint
paths between two nodes in a wrap-around butterfly network
increases exponentially with $h$;
}
\item{We present a scalable, efficient, and attack-tolerant concurrent
multipath routing algorithm on the butterfly network topology.}
\end{itemize}

This paper is organized as follows.
Section \ref{sec-related} reviews background and related work.
Section \ref{sec-ft} describes adversarial fault tolerance on
structured networks.
Section \ref{sec-butterfly} gives background on the butterfly network topology.
Section \ref{sec-bf-routing} presents our concurrent multipath routing
algorithm for the butterfly.
Section \ref{sec-discussion} discusses the results.
And Section \ref{sec-conclusion} concludes.

@@

There has been considerable work on trust in network security.
Both centralized and decentralized approaches are commonly used to create
trust infrastructures.
Centralized approaches such as {\em public key infrastructure} (PKI)
suffer from a number of vulnerabilities
\cite{ellison_ten_2000},
which stem largely from the single points of failure inherent to
centralization.
The well-known and widely-used {\em web of trust} approach
\cite{zimmermann_official_1995,ferguson_practical_2003}
is a decentralized alternative.
In a web of trust,
individuals choose who they trust initially.
Trust is then extended to new individuals if they are vouched for by a
currently-trusted individual,
making it possible to quickly establish a large group of trusted nodes.
However, web of trust's assumption of infinite transitivity is unrealistic
\cite{christianson_why_1997},
and does not distinguish between paths of different lengths.
Our work addresses both of these limitations by incorporating a more realistic
assumption of bounded trust transitivity.

Previous work on incorporating network structure into
trust models has focused on authentication
protocols, showing that independent paths can reduce an adversary's ability
to impersonate a target
\cite{levien_attack-resistant_2009}.
Other work has shown that identifying independent paths in arbitrary networks
is NP-hard and provided approximation algorithms
\cite{reiter_resilient_1998}.
Our work complements these by introducing the bounded trust transitivity assumption
extending the focus beyond authentication.
When network topology can be controlled, we sidestep the NP-hard problem of finding
independent paths on arbitrary networks by using the mathematical structure of
the butterfly topology to construct provably independent paths.

Many distributed consensus protocols (such as those used by cryptocurrencies)
are designed to tolerate arbitrary or adversarial faults.
Byzantine agreement protocols
\cite{lamport_byzantine_1982,castro_practical_1999}
provide tolerance against arbitrary faults (including attacks) under
some circumstances, but are limited to small networks due to poor scalability.
Proof-of-work \cite{dwork_pricing_1993,nakamoto_bitcoin:_2008}
and proof-of-stake \cite{king_ppcoin:_2012}
provide better scalability,
but are wasteful of computational and energy resources.
Federated Byzantine Agreement (FBA) \cite{mazieres_stellar_2015}
is scalable, allows for flexible trust,
and is highly fault-tolerant on networks meeting a set of requirements.
However, FBA does not provide a method for evaluating the
fault tolerance properties of different network structures
or for calculating the failure probabilities within a particular network.

There are relatively few attack-tolerance schemes
that focus on network structure,
compared to more popular cryptographic approaches
\cite{ferguson_practical_2003}.
All existing attack-tolerant networks we are aware of are content-addressable
networks: data is routed to and from storage nodes rather than between sender
and receiver.
Fiat and Saia described a scheme that combines the butterfly topology
with expander graphs to create a highly censorship-resistant,
content-addressable network \cite{fiat_censorship_2002},
although this scheme does not scale well and is impractical due to a
high level of data replication.
Perhaps the most mature structural solution is the Freenet collaboration
\cite{clarke_freenet:_2001}.
Freenet uses secret sharing
\cite{shamir_how_1979, blakley_safeguarding_1979}
and small-world routing
\cite{zhang_using_2002,kleinberg_small-world_2000}
to create a content-addressable network with a high level of both
confidentiality and censorship resistance.
Freenet guarantees that data is stored redundantly,
but still allows for centralized network structure,
and thus single points of failure,
as data travels from its origin to the redundant storage locations.
Unlike the above content-addressable networks, our proposal is purely network based
and does not require nodes to store data indefinitely.
Our proposal also improves on the scalablity of Fiat and Saia's work,
and does not rely on assumptions about existing social network structure.

{\em Multipath routing} protocols identify multiple paths between
source and destination
in contrast to traditional {\em unipath} routing, which uses
a single path.
The special case of {\em concurrent} multipath routing uses mutliple paths
simultaneously.
Multipath routing has many applications, including reduced congestion,
increased throughput, and more reliability
\cite{qadir_exploiting_2015}.
Many of these routing protocols offer increased confidentiality
\cite{zin_survey_2015}.
Some approaches utilize redundant paths as backups for increased
fault tolerance
\cite{alrajeh_secure_2013},
and some specifically protect against adversarial faults
\cite{kohno_improvement_2012, khalil_unmask:_2010, lou_h-spread:_2006}.
Most work on multipath routing has been motivated by applications related to
wireless sensor networks (WSNs),
and have thus focused on ad hoc, unstructured networks, often having a central
base station.
The method of Liu et al.
\cite{liu_secure_2012}
routes multiple messages first to random peers and then
to a central base station,
with the network edges constrained by sensors' physical location.
We have found only few examples in the existing literature of applications of
concurrent multipath routing to {\em adversarial} fault tolerance,
and all have focused on ad-hoc wireless sensor networks, without attention
to the role of network structure.
The alogorithm we present for the butterfly topology complements existing work
by addressing cases where links are not constrained by physical
distance,
and where network structure can be engineered for greater attack-tolerance.

@@

\begin{table*}[t!]
\caption{Comparison of attack-tolerant network communication architectures.\label{tab:compare}}
\begin{center}
\begin{tabular}{l|ccccc}
                              & Decentralized & Trust-based & Bounded-trust & Topological & Point-to-point \\
\hline
Public Key Infrastructure     &               & \cmark      & \cmark        &             & \cmark     \\
Web of Trust                  & \cmark        & \cmark      &               &             & \cmark     \\
Freenet                       & \cmark        & \cmark      & \cmark        &             &            \\
Federated Byzantine Agreement & \cmark        & \cmark      & \cmark        &             & \cmark     \\
Blockchain                    & \cmark        &             & \cmark        &             &            \\
Fiat-Saia                     & \cmark        & \cmark      & \cmark        & \cmark      &            \\
Structured Multipath FT       & \cmark        & \cmark      & \cmark        & \cmark      & \cmark     \\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

Within the field of {\em fault tolerance},
many techniques have been developed for building reliable systems
out of unreliable components
\cite{avizienis_basic_2004, von_neumann_probabilistic_1956}.
We will make use of standard fault tolerance terminology, summarized here.
A {\em fault} is said to occur when one component
of a system behaves incorrectly (e.g., a routing node blocks or
alters a message).
The result of that fault (e.g., a recipient receiving conflicting messages)
is called an {\em error} state.
If the error is undetected or corrected to the wrong value, the system is
said to have experienced a {\em failure} (e.g., an altered message is
accepted as authentic).
Note that when an error is detected but cannot be corrected,
the system has still tolerated the fault because it has not accepted an error
state.
We are concerned in particular with {\em adversarial faults},
which are chosen strategically to maximize the likelihood of a failure.

@@

Once we have determined a network's effective redundancy,
we can apply redundancy-based fault tolerance techniques,
by sending multiple copies of a message
({\em concurrent multipath routing}).
Having found the effective redundancy between two nodes,
we can simplify our model, replacing independent paths through the
complex network with direct channels between the endpoints.
We model our sender (Alice) and receiver (Bob) as
communicating over $\delta_h$ direct and redundant virtual channels.
The partial trust model allows us to make this simplifying assumption
for analyzing a fault tolerance scheme,
but implementing such a scheme will require a method for constructing
specific network paths.
We will return to the question of constructing paths in the next section.
For now, we concern ourselves with the question:
given that the network provides $\delta_h$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after inducing a fixed number of faults?

@@

In a more sophisticated multipath fault tolerance scheme,
Alice randomly chooses $k \leq \delta_h$ channels and sends a copy of
her message on each.
We assume that Mal is capable of compromising $l \leq \delta_h$ channels.
Since Alice chooses channels randomly,
all channels are equally likely to contain a message,
so Mal can do no better than also choosing randomly.
We can also return to the full network setting by noting that each of the
$\delta_h$ independent paths in the network can serve as independent channels
between Alice and Bob.
Mal's best strategy is now to identify a minimum node cut in the network
and randomly compromise nodes from that cut.
With this strategy, each compromised node reduces effective redundancy by one,
equivalent to compromising one of the channels between Alice and Bob.
If $k > l$, at least one message will get through uncompromised and all
errors are detectable.
Otherwise, the probability of Mal producing an undetectable error is
the probability that all of Alice's chosen channels are compromised:
\beq
\label{eq:pf}
p_f &=& \frac{l!(\delta_h-k)!}{\delta_h!(l-k)!}.
\eeq
Letting $k=\alpha \delta_h$ and $l=\beta \delta_h$, then applying Stirling's
approximation gives:
\begin{eqnarray}
\label{eq:pf_approx}
p_f &\approx&
\frac{\sqrt{\beta(1-\alpha)}}{\sqrt{\beta-\alpha}}
\left[
    \left( \frac{\beta-\alpha}{1-\alpha} \right)^{\alpha}
    \left( \frac{\beta}{\beta-\alpha} \right)^{\beta}
    (1-\alpha)
\right]^{\delta_h}.
\end{eqnarray}

Figure \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Equation (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
redundant paths actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with the effective redundancy $\delta_h$
(which we will later see increases exponentially in $h$ in the
butterfly topology).
This result is significant because $\delta_h$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of copies
sent $k$ is a small fraction of the effective redundancy}.
In other words, this scheme exhibits a {\em stabilizing asymmetry}:
senders can tolerate attacks from significantly more powerful
adversaries,
as long as the network structure provides large $\delta_h$.

In order to derive the above results,
we have assumed that Alice and all
intermediary agents are able to identify specific,
independent network paths that achieve the effective redundancy $\delta_h$.
We now proceed to describe a routing algorithm for doing so in the special case
of the butterfly network topology.

@@

\subsection{Partial Trust Model}

A central question in large-scale, secure communication is this:
how can two parties communicate reliably and securely
when no direct trusted link exists between them?
The commonly-used web of trust approach
\cite{zimmermann_official_1995,ferguson_practical_2003}
extends trust infinitely transitively:
to friends of friends, and friends of friends of friends, and so on.
However, the assumption of infinitely transitive trust is unrealistic
\cite{christianson_why_1997},
and does not allow for the analysis of the effects of network structure.

An alternative assumption might be that each hop away from Alice in
in the network
reduces the probability that a node can resist compromise exponentially.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
The above model can be further
approximated by assuming that nodes up to some fixed number
of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

We define the {\em partial trust model} on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing commiunicating agents,
and with edges representing mutually trusted communication links.
Let $v \in V$ be an arbitrary sender (Alice)
and $w \in V$ be an arbitrary receiver (Bob).
We assume the presence of an adversary (Mal) who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that Mal is an adversary of Alice and/or Bob specifically,
rather than the network as a whole.
So Mal can compromise any node except for those trusted by Alice or Bob.
We define a {\em trust radius} $h$ such that nodes $u$ and
$u^\prime$ trust each other if their distance is less than $h$.
For a given node $u$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(u)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(u)$:
\beq
T_h(u) &=& \left\{ u^\prime \mid d(u,u^\prime) < h \right\} \\
B_h(u) &=& \left\{ u^\prime \mid d(u,u^\prime) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $u$ from the rest of the network.
These trust assumptions imply that when Alice sends a message to Bob,
Mal can only cause faults in the set of nodes outside both of their trusted
neighborhoods: $V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.

@@

In previous sections, we showed that reliable communication across a network
can be achieved even when any single message path might be compromised by
an adversary,
provided the network has sufficient redundancy,
and provided the sender and intermediaries know how to route message
copies along independent paths.
In this section, we address both requirements by proposing a novel routing
algorithm for constructing independent paths on the butterfly network topology.
This architecture and routing algorithm achieve an
effective redundancy that increases exponentially with the trust radius,
allowing a very high level of adversarial fault tolerance.

The structure of the butterfly network is highly constrained,
making it most suitable for applications where portions of the
network structure can be designed or dictated.
Examples of such networks include:
overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
However, when attack-tolerance is desired,
it will always require control over network structure in order to
eliminate single points of failure.
The regular structure of the butterfly is not a limitation of our approach,
but rather a reflection of the inherent difficulty of attack-tolerance.
Lastly, we note that the partial trust model and multipath fault tolerance
schemes of the previous section do not rely on any particular network
topology or routing algorithm,
and our choice of the butterfly topology is only one of many possible choices.

@@

The structure of the butterfly network lends itself to a well-known
(unipath) routing algorithm,
which we later extend to the multipath case.
The unipath algorithm first follows a down or down-right edge at every step,
increasing the level $l$ by 1 and cycling through the
indices of the place-within-level.
If the current node's place-within-level matches the destination node's at
index $l$,
a down edge is chosen and the place-within-level does not change.
Otherwise, a down-right edge is chosen and the $l$th component of the
place-within-level is flipped,
after which it matches the destination.
After $m$ iterations of this, all levels have been visited
and the place-within-level matches that of the destination.
Simply following down (or up) edges will then increment (decrement) the
level until the destination node is reached.

>>>>

Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure
to censorship and surveillance.
This paper presents several contributions towards advancing those goals.
While our work is motivated by the network of internet routers,
the results are theoretical,
and can potentially be applied to many different types of networks,
whether made of physical wires, virtual tunnels,
or other types of links.

@@

Under the above assumptions,
we show how to evaluate the influence of network structure
on attack-tolerance.
We next present a structured multipath fault tolerance (SMFT) to extend
standard fault tolerance techniques to the case of adversarial faults in
networks
\cite{avizienis_basic_2004, von_neumann_probabilistic_1956}.
The SMFT scheme requires the existence of a
concurrent multipath routing (CMR) algorithm
\cite{zin_survey_2015, qadir_exploiting_2015, khiani_comparative_2013},
to takes advantage of the independence of faults
along {\em independent paths}.
We also present a novel CMR algorithm for the butterfly network topology.
The butterfly topology is popular in parallel processing
\cite{kshemkalyani_distributed_2008} and
peer-to-peer \cite{lua_survey_2005, korzun_structured_2013}
applications, due to its regular structure, low degree, and high connectivity.

It is important to note that the butterfly is a highly structured and constrained
network topology,
very different form those found in social networks and other
self-organized networks.
The reader may wonder whether it is realistic or useful to assume such control over
the network structure.
We have already seen that whenever a single point of failure exists in the network,
there is a potential for an attacker to exploit it through coercion.
So, {\em attack-tolerance cannot be achieved without the ability to influence
network structure}.
Luckily, there are scenarios in which network topology can be dictated.
Examples include overlay networks
\cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
In general,
{\em when the need for attack-tolerance is high enough to warrant investment
in infrastructure, networks can be engineered and maintained as infrastructure}.
It is also worth noting that attack-tolerant networks may be sub-components of
larger, less-constrained systems.
For example, a single server might be replaced by a distributed network of servers,
each with different ownership, physical location, and legal jurisdiction,
without placing any unrealistic constraints on the clients connecting to
those servers.

Our main contributions are:
\begin{itemize}
\item{
We propose a novel structured multipath fault tolerance (SMFT) scheme
for extending standard fault tolerance techniques to
{\em adversarial} faults in {\em complex networks}.
We do so by modeling redundant {\em independent paths}
with {\em bounded trust transitivity} as a single virtual channel,
and show that the probability of detecting adversarial faults
approaches 1 exponentially with the number of paths;
}
\item{We prove that the number of $h$-internal vertex disjoint
paths between two nodes in a wrap-around butterfly network
increases exponentially with $h$,
and thus that the number of independent paths in a network
increases exponentially with the level of trust transitivity;
}
\item{We present a scalable and efficient concurrent
multipath routing (CMR) algorithm on the butterfly network topology,
which can be combined with SMFT to achieve a high level of attack tolerance.}
\end{itemize}

This paper is organized as follows.
Section \ref{sec-related} reviews background and related work.
Section \ref{sec-ft} describes adversarial fault tolerance on
structured networks.
Section \ref{sec-butterfly} gives background on the butterfly network topology.
Section \ref{sec-bf-route} presents our concurrent multipath routing
algorithm for the butterfly.
Section \ref{sec-discussion} discusses the results.
And Section \ref{sec-conclusion} concludes.

@@

There has been considerable work on trust-based attack-tolerance techniques
in network security, both centralized and decentralized.
Centralized approaches such as {\em public key infrastructure} (PKI)
suffer from a number of vulnerabilities
\cite{ellison_ten_2000}, including vulnerability to coercion,
which stems largely from the single points of failure inherent to
centralization.
The well-known and widely-used {\em web of trust} approach
\cite{zimmermann_official_1995,ferguson_practical_2003}
is a decentralized alternative.
In a web of trust,
individuals choose who they trust initially.
Trust is then extended to new individuals if they are vouched for by a
currently-trusted individual.
Infinite trust transitivity is helpful for establishing a large group of
trusted nodes, but unfortunately unrealistic
\cite{christianson_why_1997}.
Additionally, the web of trust approach
does not distinguish between paths of different lengths.
Our work addresses both of these limitations by requiring only
bounded trust transitivity.

Previous work applying network topology to attack tolerance has
focused on authentication,
showing that independent paths can reduce an adversary's ability
to impersonate a target
\cite{levien_attack-resistant_2009}.
Other work has shown that identifying independent paths in arbitrary networks
is NP-hard and provided approximation algorithms
\cite{reiter_resilient_1998}.
Our work complements these results by extending our focus beyond authentication,
to communication.
When network topology can be controlled, we sidestep the NP-hard problem of finding
independent paths on arbitrary networks by using the mathematical structure of
the butterfly topology to construct provably independent paths.

Many distributed consensus protocols (such as those used by cryptocurrencies)
are designed to tolerate arbitrary or adversarial faults.
Byzantine agreement protocols
\cite{lamport_byzantine_1982,castro_practical_1999}
provide tolerance against arbitrary faults (including attacks) under
some circumstances, but are limited to small networks due to poor scalability.
Proof-of-work \cite{dwork_pricing_1993,nakamoto_bitcoin:_2008} (blockchain)
systems provide better scalability,
but are wasteful of computational and energy resources,
and do not take advantage of trusted relationships.
Federated Byzantine Agreement (FBA) \cite{mazieres_stellar_2015}
is scalable, allows for flexible trust,
and is highly fault-tolerant on networks meeting specific requirements.
However, FBA does not provide a method for constructing networks to meet
those requirements,
or for calculating the failure probabilities within a particular network.

All existing attack-tolerant networks we are aware of are content-addressable
networks (CANs) in which data is stored and retrieved based on key values,
rather than point-to-point networks, in which data is communicated between
two parties.
Fiat and Saia described a scheme that combines the butterfly topology
with expander graphs to create a highly censorship-resistant,
content-addressable network \cite{fiat_censorship_2002},
although this scheme does not scale well and is impractical due to a
high level of data replication.
Perhaps the most mature structural solution is the Freenet collaboration
\cite{clarke_freenet:_2001}.
Freenet uses secret sharing
\cite{shamir_how_1979, blakley_safeguarding_1979}
and small-world routing
\cite{zhang_using_2002,kleinberg_small-world_2000}
to create a content-addressable network with a high level of both
confidentiality and censorship resistance.
Freenet guarantees that data is stored redundantly,
but still allows for centralized network structure,
and thus single points of failure,
as data travels from its origin to the redundant storage locations.
Unlike the above content-addressable networks, our architecture is purely network based
and does not require nodes to store data indefinitely.
Our architecture also improves on the scalablity of the Fiat-Saia network,
and makes requirements about network topology explicit.

{\em Multipath routing} protocols identify multiple paths between
source and destination
in contrast to traditional {\em unipath} routing, which uses
a single path.
The special case of {\em concurrent} multipath routing uses mutliple paths
simultaneously.
Multipath routing has many applications, including reduced congestion,
increased throughput, and more reliability
\cite{qadir_exploiting_2015}.
Many of these routing protocols offer increased confidentiality
\cite{zin_survey_2015}.
Some approaches utilize redundant paths as backups for increased
fault tolerance
\cite{alrajeh_secure_2013},
and some specifically protect against adversarial faults
\cite{kohno_improvement_2012, khalil_unmask:_2010, lou_h-spread:_2006}.
Most work on multipath routing has been motivated by applications related to
wireless sensor networks (WSNs),
and have thus focused on ad hoc, unstructured networks, often having a central
base station.
The method of Liu et al.
\cite{liu_secure_2012}
routes multiple messages first to random peers and then
to a central base station,
with the network edges constrained by sensors' physical location.
We have found very few examples of CMR applied to {\em adversarial}
fault tolerance in the existing literature,
and all have focused on ad-hoc wireless sensor networks, without attention
to the role of network structure.
The alogorithm we present for the butterfly topology complements existing work
by addressing cases where links are not constrained by physical
distance,
and where network structure can be engineered for greater attack-tolerance.

@@

Our proposed architecture is differentiated from existing systems by several
properties (Table \ref{tab:compare}).
Decentralized architectures are more resistent to coercion
\cite{grewal_caveat_2013}
and man-in-the-middle attacks \cite{nayak_different_2010}.
Trust-based systems are more sustainable than proof-of-work.
Bounded-trust systems do not require the unrealistic assumption of infinite
trust transitivity.
Topological approaches address the root cause of vulnerability
in heavy-tail networks,
rather than relying on technology that can be side-stepped through coercion.
Point-to-point communication allows two individuals to exchange messages
without requiring large amounts of indefinite data storage on intermediate
nodes.

\begin{table*}[t!]
\caption{Comparison of attack-tolerant network communication architectures.\label{tab:compare}}
\begin{center}
\begin{tabular}{l|ccccc}
                              & Decentralized & Trust-based & Bounded-trust & Topological & Point-to-point \\
\hline
Public Key Infrastructure     &               & \cmark      & \cmark        &             & \cmark     \\
Web of Trust                  & \cmark        & \cmark      &               &             & \cmark     \\
Freenet                       & \cmark        & \cmark      & \cmark        &             &            \\
Federated Byzantine Agreement & \cmark        & \cmark      & \cmark        &             & \cmark     \\
Proof of Work/Blockchain      & \cmark        &             & \cmark        &             &            \\
Fiat-Saia                     & \cmark        & \cmark      & \cmark        & \cmark      &            \\
Structured Multipath FT       & \cmark        & \cmark      & \cmark        & \cmark      & \cmark     \\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

Within the field of {\em fault tolerance},
many techniques have been developed for building reliable systems
out of unreliable components
\cite{avizienis_basic_2004, von_neumann_probabilistic_1956}.
We will make use of standard fault tolerance terminology, summarized here.
A {\em fault} is occurs when one component
of a system behaves incorrectly (e.g., a routing node blocks or
alters a message).
The result of that fault (e.g., a recipient receiving conflicting messages)
is an {\em error} state.
If the error is undetected or corrected to the wrong value,
the system has experienced a {\em failure} (e.g., an altered message is
accepted as authentic).
Note that when an error is detected but cannot be corrected,
the system has still tolerated the fault because it has not accepted an error
state.
We are concerned in particular with {\em adversarial faults},
which are chosen strategically to maximize the likelihood of a failure.

@@

Standard fault tolerance methods use redundancy to detect and correct
statistically indpendent faults.
In complex networks however, faults can be correlated when,
for example, two messages pass through the same faulty node.
For now, let us assume our sender (Alice) and receiver (Bob) are connected
by $\delta_h$ direct channels, with indpendent errors.
We will return to the question of constructing these channels in subsequent
sections.
For now, we concern ourselves with the question:
given that the network provides $\delta_h$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after causing faults in a fixed number of channels?

@@

In a more sophisticated multipath fault tolerance scheme,
Alice randomly chooses $k \leq \delta_h$ channels and sends a copy of
her message on each.
We assume that Mal is capable of compromising $l \leq \delta_h$ channels.
Since Alice chooses channels randomly,
all channels are equally likely to contain a message,
so Mal can do no better than also choosing randomly.
If $k > l$, at least one message will get through uncompromised and all
errors are detectable.
Otherwise, the probability of Mal producing an undetectable error is
the probability that all of Alice's chosen channels are compromised:
\beq
\label{eq:pf}
p_f &=& \frac{l!(\delta_h-k)!}{\delta_h!(l-k)!}.
\eeq
Letting $k=\alpha \delta_h$ and $l=\beta \delta_h$, then applying Stirling's
approximation gives:
\begin{eqnarray}
\label{eq:pf_approx}
p_f &\approx&
\frac{\sqrt{\beta(1-\alpha)}}{\sqrt{\beta-\alpha}}
\left[
    \left( \frac{\beta-\alpha}{1-\alpha} \right)^{\alpha}
    \left( \frac{\beta}{\beta-\alpha} \right)^{\beta}
    (1-\alpha)
\right]^{\delta_h}.
\end{eqnarray}

Figure \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Equation (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
channels actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with $\delta_h$.
This result is significant because,
as we will soon show, $\delta_h$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of channels used
$k$ is a small fraction of the channels available}
In other words, this scheme exhibits a {\em stabilizing asymmetry}:
senders can tolerate attacks from significantly more powerful
adversaries,
as long as the network provides large $\delta_h$.

@@

\subsection{Bounded Trust Model}

So far, we have assumed that Alice and Bob have access to some number
$\delta_h$ of channels with statistically indpendent faults.
However, in real communication architectures, direct links between all
pairs of individuals are intractable and messages must be routed through
a number of intermediate nodes.
In an adversarial setting,
the existence of intermediate nodes introduces two problems:
1. intermediate nodes may be compromised by the adversary and
2. faults on paths are no longer uncorrelated: two paths may pass through the
same compromised node.
We show how to how to resolve these problems using a combination of network
structure and bounded trust transitivity.

Trust-based approaches to secure communication assume that some parties
cannot be compromised.
One common approach, the web of trust
\cite{zimmermann_official_1995,ferguson_practical_2003},
extends trust infinitely transitively:
Alice trusts her friends, as well as her friends' friends, and so on.
However, the assumption of infinitely transitive trust is unrealistic
\cite{christianson_why_1997}.
Furthermore, infinite trust transitivity does not allow for analysis of
network strucutre; all that matters is whether some path exists,
rather than the number of paths and their structure.

An alternative assumption might be that each hop away from Alice in
in the network
reduces the probability that a node can resist compromise exponentially.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
The above model can be further
simplified by assuming that nodes up to some fixed number
of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

We define the {\em bounded trust model} on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing commiunicating parties,
with edges representing mutually trusted communication links.
We define a {\em trust radius} $h$ such that nodes $v$ and
$w$ trust each other if their distance is less than $h$.
For a given node $v$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $v$ from the rest of the network.

Now let $s \in V$ be an arbitrary sender
and $t \in V$ be an arbitrary receiver.
We assume the presence of an adversary who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that the adversary is specifically targeting communicaiton
between $s$ and $t$ and
can compromise any node except for those trusted by $s$ or $t$.
Under these trust assumptions, adversarial faults can only occur
outside the trusted neighborhoods of $s$ and $t$:
$V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.

@@

In order to implement structured multipath fault tolerance,
we need a strucutred network topology with high effective redundancy.
In this paper, we apply SMFT to the butterfly network topology
\cite{kshemkalyani_distributed_2008}.
The structure of the butterfly network is highly constrained,
making it most suitable for applications where portions of the
network structure can be designed or dictated.
Examples of such networks include:
overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.
However, when attack-tolerance is desired,
it will always require control over network structure in order to
eliminate single points of failure.
The regular structure of the butterfly is not a limitation of our approach,
but rather a reflection of the inherent difficulty of attack-tolerance.
To address the case when the network cannot be fully controlled,
we show how partially rewiring a snapshot of the internet's router
network can greatly increase it's effective redundancy and
attack-tolerance properties.

@@

The structure of the butterfly network lends itself to a well-known
(unipath) routing algorithm (Figure \ref{fig:bf-route}),
which we later extend to the multipath case.
The unipath algorithm first follows a down or down-right edge at every step,
increasing the level $l$ by 1 and cycling through the
indices of the place-within-level.
If the current node's place-within-level matches the destination node's at
index $l$,
a down edge is chosen and the place-within-level does not change.
Otherwise, a down-right edge is chosen and the $l$th component of the
place-within-level is flipped,
after which it matches the destination.
After $m$ iterations of this, all levels have been visited
and the place-within-level matches that of the destination.
Simply following down (or up) edges will then increment (decrement) the
level until the destination node is reached.

\subsection{Butterfly Rewiring}

\begin{figure*}[h!]
\centerline{\includegraphics[width=7in,height=1.75in]{fig-mincut}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The effective redundancy is shown for several values of trust transitivity $h$.
For $h>0$, the original network has higher effective redundancy up to a crossover point,
after which the rewired network performs better.
}
\label{fig:mincut}
\end{figure*}
